---
title: "CMJ no plots"
author: "Dan Feeney"
date: "February 6, 2019"
output: html_document
---


```{r}
rm(list=ls())
setwd("C:/Users/Daniel.Feeney/Dropbox (Boa)/2018 BOA Nonlinear Segment Performance/Analysis")

s5 <- read.csv("C:/Users/Daniel.Feeney/Dropbox (Boa)/2018 BOA Nonlinear Segment Performance/Analysis/AllSubResults.csv")

#load bootstrapping package, create functions to calcualte the metrics with a resample
library(boot)
library(ggplot2)
sampleMean <- function(x, d) {
  return(mean(x[d]))
}

conInterval_simple <- function(x){
  err <- qt(0.975, df=length(x) - 1) * sd(x)/sqrt(length(x))
  return(err)
}

set.seed(5280)
```

## Bootstrap the differences somewhat generic function. One for each comparison
```{r}
confidenceDifferences_m <- function(df, metric, num_boots) {
  C1_ap <- subset(df[,metric], df$Condition == 'M' & df$Movement == 'CMJ')
  LC_ap <- subset(df[,metric], df$Condition == 'S' & df$Movement == 'CMJ')

  mean_differences <- vector('numeric', 10000)

  for (i in 1:10000) {
    C1_tmp <- sample(C1_ap, length(C1_ap), replace=TRUE)
    LC_tmp <- sample(LC_ap, length(C1_ap), replace=TRUE)
    mean_differences[i] <- mean(C1_tmp - LC_tmp)
  }

  mean(mean_differences)
  conInterval_simple(mean_differences)
  summary(mean_differences)


  return(list(quantile(mean_differences,probs=c(.125,.875)), quantile(mean_differences,probs=c(0.05, 0.95))))
}

confidenceDifferences_l <- function(df, metric, num_boots) {
  C1_ap <- subset(df[,metric], df$Condition == 'L' & df$Movement == 'CMJ')
  LC_ap <- subset(df[,metric], df$Condition == 'S' & df$Movement == 'CMJ')

  mean_differences <- vector('numeric', 10000)

  for (i in 1:10000) {
    C1_tmp <- sample(C1_ap, length(C1_ap), replace=TRUE)
    LC_tmp <- sample(LC_ap, length(C1_ap), replace=TRUE)
    mean_differences[i] <- mean(C1_tmp - LC_tmp)
  }

  mean(mean_differences)
  conInterval_simple(mean_differences)
  summary(mean_differences)

  return(list(quantile(mean_differences,probs=c(.125,.875)), quantile(mean_differences,probs=c(0.05, 0.95))))
}

confidenceDifferences_t <- function(df, metric, num_boots) {
  C1_ap <- subset(df[,metric], df$Condition == 'T' & df$Movement == 'CMJ')
  LC_ap <- subset(df[,metric], df$Condition == 'S' & df$Movement == 'CMJ')

  mean_differences <- vector('numeric', 10000)

  for (i in 1:10000) {
    C1_tmp <- sample(C1_ap, length(C1_ap), replace=TRUE)
    LC_tmp <- sample(LC_ap, length(C1_ap), replace=TRUE)
    mean_differences[i] <- mean(C1_tmp - LC_tmp)
  }

  mean(mean_differences)
  conInterval_simple(mean_differences)
  summary(mean_differences)


  return(list(quantile(mean_differences,probs=c(.125,.875)), quantile(mean_differences,probs=c(0.05, 0.95))))
}

```


# Test Time on FP. Positive difference is a low score, negative is a high score
## Look at averages for each condition for CMJ
```{r}
cmj <- subset(s5, s5$Movement == 'CMJ' & s5$ï..Subject == 4)

tapply(cmj$Time.on.FP, cmj$Condition, FUN = mean)
tapply(cmj$Time.on.FP, cmj$Condition, FUN = sd)

contactTime <- ggplot(cmj, aes(x = Condition, y = abs(Time.on.FP))) + geom_bar(stat='summary', fun.y='mean') +
    geom_pointrange(stat = "summary", fun.data = "mean_se",
                  position = position_dodge(width = 0.9)) 
contactTime +   theme(axis.text=element_text(size=12),
                  axis.title=element_text(size=14,face="bold")) + labs(title="Sub 5",x="Configuration", y = "Time on FP")
```
## For CMJ
### all three stay 0
```{r}
confidenceDifferences_m(cmj, 6, 10000)
confidenceDifferences_l(cmj, 6, 10000)
confidenceDifferences_t(cmj, 6, 10000)

```


# Test total GRF RFD avg eccentric. Positive differences are (+) Negative (-)
## Lets start by looking at averages for each condition for Skater and CMJ
```{r}
tapply(cmj$Total.GRF.RFD.Avg.Eccentric, cmj$Condition, FUN = mean)

RFD_avg <- ggplot(cmj, aes(x = Condition, y = abs(Total.GRF.RFD.Avg.Eccentric))) + geom_bar(stat='summary', fun.y='mean') +
    geom_pointrange(stat = "summary", fun.data = "mean_se",
                  position = position_dodge(width = 0.9)) 
RFD_avg +   theme(axis.text=element_text(size=12),
                  axis.title=element_text(size=14,face="bold")) + labs(title="Sub 5",x="Configuration", y = "Avg RFD Eccentric")
```


```{r}
confidenceDifferences_m(cmj, 7, 10000)
confidenceDifferences_l(cmj, 7, 10000)
confidenceDifferences_t(cmj, 7, 10000)

```


# Test total GRF peak. Positive differences are (+) negative are (-)
## Lets start by looking at averages for each condition for Skater and CMJ
```{r}
tapply(cmj$Total.GRF.Peak, cmj$Condition, FUN = mean)

GRF_peak <- ggplot(cmj, aes(x = Condition, y = abs(Total.GRF.Peak))) + geom_bar(stat='summary', fun.y='mean') +
    geom_pointrange(stat = "summary", fun.data = "mean_se",
                  position = position_dodge(width = 0.9)) 
GRF_peak +   theme(axis.text=element_text(size=12),
                  axis.title=element_text(size=14,face="bold")) + labs(title="Sub 5",x="Configuration", y = "Peak GRF")
```

### all stay 0
```{r}
confidenceDifferences_m(cmj, 8, 10000)
confidenceDifferences_l(cmj, 8, 10000)
confidenceDifferences_t(cmj, 8, 10000)

```


# Test COM peak power propulsive. Positive are (+) negative are (-)
## Lets start by looking at averages for each condition for Skater and CMJ
```{r}
tapply(cmj$COM.Power.Peak.Propulsive, cmj$Condition, FUN = mean)

Pwr_peak <- ggplot(cmj, aes(x = Condition, y = abs(COM.Power.Peak.Propulsive))) + geom_bar(stat='summary', fun.y='mean') +
    geom_pointrange(stat = "summary", fun.data = "mean_se",
                  position = position_dodge(width = 0.9))  
Pwr_peak +   theme(axis.text=element_text(size=12),
                  axis.title=element_text(size=14,face="bold")) + labs(title="Sub 5",x="Configuration", y = "Peak COM Power Propulsive")

    
```


```{r}
confidenceDifferences_m(cmj, 9, 1000)
confidenceDifferences_l(cmj, 9, 1000)
confidenceDifferences_t(cmj, 9, 1000)

```

# Test COM work eccentric. Positive are (+) negative are (-)
## Lets start by looking at averages for each condition for Skater and CMJ
```{r}
tapply(cmj$COM.Work.Eccentric, cmj$Condition, FUN = mean)

Work_ecc <- ggplot(cmj, aes(x = Condition, y = COM.Work.Eccentric)) + geom_bar(stat='summary', fun.y='mean') +
    geom_pointrange(stat = "summary", fun.data = "mean_se",
                  position = position_dodge(width = 0.9)) 
Work_ecc +   theme(axis.text=element_text(size=12),
                  axis.title=element_text(size=14,face="bold")) + labs(title="Sub 5",x="Configuration", y = "COM Work Eccentric")
```


```{r}
confidenceDifferences_m(cmj, 10, 10000)
confidenceDifferences_l(cmj, 10, 10000)
confidenceDifferences_t(cmj, 10, 10000)

```

# Test COM work propulsive
## Lets start by looking at averages for each condition for Skater and CMJ
```{r}
tapply(cmj$COM.Work.Propulsive, cmj$Condition, FUN = mean)

Work_prop <- ggplot(cmj, aes(x = Condition, y = abs(COM.Work.Propulsive))) + geom_bar(stat='summary', fun.y='mean') +
    geom_pointrange(stat = "summary", fun.data = "mean_se",
                  position = position_dodge(width = 0.9)) 
Work_prop +   theme(axis.text=element_text(size=12),
                  axis.title=element_text(size=14,face="bold")) + labs(title="Sub 5",x="Configuration", y = "COM Work Propulsive")
```


```{r}
confidenceDifferences_m(cmj, 11, 10000)
confidenceDifferences_l(cmj, 11, 10000)
confidenceDifferences_t(cmj, 11, 10000)

```