---
title: "CMJ automated"
author: "Dan Feeney"
date: "February 6, 2019"
output: html_document
---


```{r}
rm(list=ls())

s5 <- read.csv("C:/Users/Daniel.Feeney/Dropbox (Boa)/2018 BOA Nonlinear Segment Performance/Analysis/AllSubResults.csv")
names(s5)[1]<-"Subject"

#load bootstrapping package, create functions to calcualte the metrics with a resample
library(boot)
library(ggplot2)
sampleMean <- function(x, d) {
  return(mean(x[d]))
}

conInterval_simple <- function(x){
  err <- qt(0.975, df=length(x) - 1) * sd(x)/sqrt(length(x))
  return(err)
}

set.seed(5280)
```

## Bootstrap the differences somewhat generic function. One for each comparison
```{r}
confidenceDifferences_m <- function(df, metric, num_boots) {
  C1_ap <- subset(df[,metric], df$Condition == 'M' & df$Movement == 'CMJ')
  LC_ap <- subset(df[,metric], df$Condition == 'S' & df$Movement == 'CMJ')

  mean_differences <- vector('numeric', 10000)

  for (i in 1:10000) {
    C1_tmp <- sample(C1_ap, length(C1_ap), replace=TRUE)
    LC_tmp <- sample(LC_ap, length(C1_ap), replace=TRUE)
    mean_differences[i] <- mean(C1_tmp - LC_tmp)
  }

  foo <- quantile(mean_differences,probs=c(0.125,0.875))
  bar <- quantile(mean_differences,probs=c(0.05, 0.95))

  newList <- list("low" = foo, "high" = bar)
  return(newList)
}

confidenceDifferences_l <- function(df, metric, num_boots) {
  C1_ap <- subset(df[,metric], df$Condition == 'L' & df$Movement == 'CMJ')
  LC_ap <- subset(df[,metric], df$Condition == 'S' & df$Movement == 'CMJ')

  mean_differences <- vector('numeric', 10000)

  for (i in 1:10000) {
    C1_tmp <- sample(C1_ap, length(C1_ap), replace=TRUE)
    LC_tmp <- sample(LC_ap, length(C1_ap), replace=TRUE)
    mean_differences[i] <- mean(C1_tmp - LC_tmp)
  }

  foo <- quantile(mean_differences,probs=c(0.125,0.875))
  bar <- quantile(mean_differences,probs=c(0.05, 0.95))

  newList <- list("low" = foo, "high" = bar)
  return(newList)
}

confidenceDifferences_t <- function(df, metric, num_boots) {
  C1_ap <- subset(df[,metric], df$Condition == 'T' & df$Movement == 'CMJ')
  LC_ap <- subset(df[,metric], df$Condition == 'S' & df$Movement == 'CMJ')

  mean_differences <- vector('numeric', 10000)

  for (i in 1:10000) {
    C1_tmp <- sample(C1_ap, length(C1_ap), replace=TRUE)
    LC_tmp <- sample(LC_ap, length(C1_ap), replace=TRUE)
    mean_differences[i] <- mean(C1_tmp - LC_tmp)
  }

  foo <- quantile(mean_differences,probs=c(0.125,0.875))
  bar <- quantile(mean_differences,probs=c(0.05, 0.95))

  newList <- list("low" = foo, "high" = bar)
  return(newList)
}

calc_Category <- function(dat){

  valStart <- 0
  
  if (dat$high[1] < 0 && dat$high[2] < 0) {
    valStart = 2
  } else if (dat$low[1] < 0 && dat$low[2] < 0) {
    valStart = 1
  } else if (dat$low[1] > 0 && dat$low[2] > 0) {
    valStart = -1
  } else if (dat$high[1] > 0 && dat$high[2] > 0) {
    valStart = -2
  } 
  
  return(valStart)
}

calc_Category_pos <- function(dat){

  valStart <- 0
  
  if (dat$high[1] > 0 && dat$high[2] > 0) {
    valStart = 2
  } else if (dat$low[1] > 0 && dat$low[2] > 0) {
    valStart = 1
  } else if (dat$low[1] < 0 && dat$low[2] < 0) {
    valStart = -1
  } else if (dat$high[1] < 0 && dat$high[2] < 0) {
    valStart = -2
  } 
  
  return(valStart)
}


```


# Test Time on FP. Positive difference is a low score, negative is a high score
```{r}
cmj <- subset(s5, s5$Movement == 'CMJ')
no_Subs <- length(unique(cmj$Subject))

mCategorical_score <- numeric(length(unique(cmj$Subject)))
lCategorical_score <- numeric(length(unique(cmj$Subject)))
tCategorical_score <- numeric(length(unique(cmj$Subject)))


count_var <- 1
for (subNo in unique(cmj$Subject)) {
  
  tmp_sub <- subset(cmj, cmj$Subject == subNo)
  
  mVals <- confidenceDifferences_m(tmp_sub, 6, 10000)
  lVals <- confidenceDifferences_l(tmp_sub, 6, 10000)
  tVals <- confidenceDifferences_t(tmp_sub, 6, 10000)
  
  mCategorical_score[count_var] <- calc_Category(mVals)
  lCategorical_score[count_var] <- calc_Category(lVals)
  tCategorical_score[count_var] <- calc_Category(tVals)
  
  count_var <- count_var + 1
  
}


results <- as.data.frame(cbind(as.vector(cbind(rep('L',length(lCategorical_score)), rep('M',length(mCategorical_score)), rep('T',length(tCategorical_score)))), as.vector(cbind(lCategorical_score, mCategorical_score, tCategorical_score)), as.vector(rbind(rep(unique(cmj$Subject),3)))))

names(results) <- c('Config', 'TimeonFP', 'SubNo')
results <- results[,c("SubNo", "Config", "TimeonFP")]

```


# Test total GRF RFD avg eccentric. Positive differences are (+) Negative (-)
## Lets start by looking at averages for each condition for cmjr and CMJ
```{r}

mCategorical_score <- numeric(length(unique(cmj$Subject)))
lCategorical_score <- numeric(length(unique(cmj$Subject)))
tCategorical_score <- numeric(length(unique(cmj$Subject)))


count_var <- 1
for (subNo in unique(cmj$Subject)) {
  
  tmp_sub <- subset(cmj, cmj$Subject == subNo)
  
  mVals <- confidenceDifferences_m(tmp_sub, 7, 10000)
  lVals <- confidenceDifferences_l(tmp_sub, 7, 10000)
  tVals <- confidenceDifferences_t(tmp_sub, 7, 10000)
  
  mCategorical_score[count_var] <- calc_Category_pos(mVals)
  lCategorical_score[count_var] <- calc_Category_pos(lVals)
  tCategorical_score[count_var] <- calc_Category_pos(tVals)
  
  count_var <- count_var + 1
  
}

results <- cbind(results, as.vector(cbind(lCategorical_score, mCategorical_score, tCategorical_score)))
names(results)[4] <- c('GRF_RFD_Ecc')

```


# Test total GRF peak. Positive differences are (+) negative are (-)
## Lets start by looking at averages for each condition for cmjr and CMJ
```{r}
mCategorical_score <- numeric(length(unique(cmj$Subject)))
lCategorical_score <- numeric(length(unique(cmj$Subject)))
tCategorical_score <- numeric(length(unique(cmj$Subject)))


count_var <- 1
for (subNo in unique(cmj$Subject)) {
  
  tmp_sub <- subset(cmj, cmj$Subject == subNo)
  
  mVals <- confidenceDifferences_m(tmp_sub, 8, 10000)
  lVals <- confidenceDifferences_l(tmp_sub, 8, 10000)
  tVals <- confidenceDifferences_t(tmp_sub, 8, 10000)
  
  mCategorical_score[count_var] <- calc_Category_pos(mVals)
  lCategorical_score[count_var] <- calc_Category_pos(lVals)
  tCategorical_score[count_var] <- calc_Category_pos(tVals)
  
  count_var <- count_var + 1
  
}

results <- cbind(results, as.vector(cbind(lCategorical_score, mCategorical_score, tCategorical_score)))
names(results)[5] <- c('Peak_GRF')

```


# Test COM peak power propulsive. Positive are (+) negative are (-)
## Lets start by looking at averages for each condition for cmjr and CMJ
```{r}
mCategorical_score <- numeric(length(unique(cmj$Subject)))
lCategorical_score <- numeric(length(unique(cmj$Subject)))
tCategorical_score <- numeric(length(unique(cmj$Subject)))


count_var <- 1
for (subNo in unique(cmj$Subject)) {
  
  tmp_sub <- subset(cmj, cmj$Subject == subNo)
  
  mVals <- confidenceDifferences_m(tmp_sub, 9, 10000)
  lVals <- confidenceDifferences_l(tmp_sub, 9, 10000)
  tVals <- confidenceDifferences_t(tmp_sub, 9, 10000)
  
  mCategorical_score[count_var] <- calc_Category_pos(mVals)
  lCategorical_score[count_var] <- calc_Category_pos(lVals)
  tCategorical_score[count_var] <- calc_Category_pos(tVals)
  
  count_var <- count_var + 1
  
}

results <- cbind(results, as.vector(cbind(lCategorical_score, mCategorical_score, tCategorical_score)))
names(results)[6] <- c('Peak_pwr_com')

```

# Test COM work eccentric. Positive are (+) negative are (-)
## Lets start by looking at averages for each condition for cmjr and CMJ
```{r}
mCategorical_score <- numeric(length(unique(cmj$Subject)))
lCategorical_score <- numeric(length(unique(cmj$Subject)))
tCategorical_score <- numeric(length(unique(cmj$Subject)))


count_var <- 1
for (subNo in unique(cmj$Subject)) {
  
  tmp_sub <- subset(cmj, cmj$Subject == subNo)
  
  mVals <- confidenceDifferences_m(tmp_sub, 10, 10000)
  lVals <- confidenceDifferences_l(tmp_sub, 10, 10000)
  tVals <- confidenceDifferences_t(tmp_sub, 10, 10000)
  
  mCategorical_score[count_var] <- calc_Category_pos(mVals)
  lCategorical_score[count_var] <- calc_Category_pos(lVals)
  tCategorical_score[count_var] <- calc_Category_pos(tVals)
  
  count_var <- count_var + 1
  
}

results <- cbind(results, as.vector(cbind(lCategorical_score, mCategorical_score, tCategorical_score)))
names(results)[7] <- c('Work_ecc')

```

# Test COM work propulsive
```{r}
mCategorical_score <- numeric(length(unique(cmj$Subject)))
lCategorical_score <- numeric(length(unique(cmj$Subject)))
tCategorical_score <- numeric(length(unique(cmj$Subject)))


count_var <- 1
for (subNo in unique(cmj$Subject)) {
  
  tmp_sub <- subset(cmj, cmj$Subject == subNo)
  
  mVals <- confidenceDifferences_m(tmp_sub, 11, 10000)
  lVals <- confidenceDifferences_l(tmp_sub, 11, 10000)
  tVals <- confidenceDifferences_t(tmp_sub, 11, 10000)
  
  mCategorical_score[count_var] <- calc_Category(mVals)
  lCategorical_score[count_var] <- calc_Category(lVals)
  tCategorical_score[count_var] <- calc_Category(tVals)
  
  count_var <- count_var + 1
  
}

results <- cbind(results, as.vector(cbind(lCategorical_score, mCategorical_score, tCategorical_score)))
names(results)[8] <- c('Work_prop')

results <- cbind(results, rowSums(results[4:8],))
names(results)[9] <- c('Total_Score')

tapply(results$Total_Score, results$Config, FUN=mean)

length(subset(results$Total_Score, results$Total_Score > 1 & results$Config == 'M'))
length(subset(results$Total_Score, results$Total_Score > 1 & results$Config == 'T'))
length(subset(results$Total_Score, results$Total_Score > 1 & results$Config == 'L'))

```



```{r}
a <- ggplot(results, aes(x = Total_Score)) + geom_histogram(aes(color = Config, fill = Config), alpha = 0.4, bins = 10) + scale_fill_manual(values = c("#DC582A", "#003D4C", "#00966C")) + scale_color_manual(values = c("#DC582A", "#003D4C", "#00966C")) + theme_classic()
a

p <- ggplot(results, aes(x = Config, y = Total_Score)) + geom_boxplot() + geom_dotplot(binaxis='y', stackdir='center', dotsize=1) 
p + theme_classic()

```